---
title: New England Summer 2018
author: ''
date: '2018-07-12'
slug: new-england-summer-2018
categories: []
tags: []
---


```{r, echo=FALSE, include=FALSE}
library(magick)
library(tidyquant)
library(leaflet)

```

```{r, image, message=FALSE,echo=FALSE, cache=TRUE}

ne <- image_read("~/Documents/VT_Trip/VT_trip/new_england.gif")
ne
```


## Vermont & New Hampshire Trip

### Day 1 June 29

* Landed at Newark Airport
* Ate [Roti](https://roti.com/wp-content/uploads/2018/02/RotiDC-NYCCatering021418.pdf) falafel for lunch
* Started driving toward New Haven
* Dinner at [Frank Pepe Pizza]()
* Started driving towards Barnet, VT at around 8.00 pm
* Reached the rented house at 1.30 am. It was an adventure to locate the house late at night with no cell phone reception.
* The house was impressive, location was great and it was located in the woods.
* You could hear owls at night and their sound would echo from the near by mountains.

<br>
<br>

```{r house,message=FALSE,echo=FALSE, fig.height=11,fig.width=8}
house <- image_read("~/Documents/VT_Trip/VT_trip/house.jpg")
house

```
<br>
<br>

```{r house_map, echo=FALSE}
# leaflet() %>%
#   addTiles() %>%
#   addMarkers(lng = -72.136948, lat = 44.298359, label = 'Rental House')
```


### Day 2 June 30

* Woke up at sunrise
* Had breakfast outside
* Left to see Flume Gorge falls
* Enjoyed a nice hike up to the falls
* Came home and made some important life decisions over dinner.
<br>
<br>

```{r, flume gorge, message=FALSE,echo=FALSE}

gorge <- image_read("~/Documents/VT_Trip/VT_trip/FlumeGorge.jpg")
gorge_fall <- image_read("~/Documents/VT_Trip/VT_trip/gorge_fall.jpg")
gorge_falls <- image_read("~/Documents/VT_Trip/VT_trip/gorge_falls.jpg")
gorge_track <- image_read("~/Documents/VT_Trip/VT_trip/gorge_track.jpg")

gorge_track

gorge

gorge_fall

gorge_falls

leaflet() %>%
  addTiles() %>%
  addMarkers(lng = -71.679960, lat = 44.097029, label = 'The Flume Gorge')

```
<br>
<br>

### Day 3 July 1, Canada Day

* Woke up again at sunrise (Rooms have no curtains)
* After breakfast relaxed in the morning and left for Mount Washington in the afternoon
* Ate Lunch at Chang's Thai in Littleton, enjoyed the thai tea with coconut cream
* Littleton is a charming town in New Hampshire
* Ate ice cream at Bishops home made ice cream
* Drove to Mt Washington, it is one of the coldest places on earth
* Since they had a 900 lbs weight limit, the security guard asked to lose some weight and come back
* We decided to split our group
* The drive to Mt Washington was incredible
* The road was narrow and driving was challenging
* On Mt Washington, we walked up to the summit, visited the tip top house, and hiked a little
* On the way back we visited Mt Washington Hotel
* It was the place where leaders from 44 nations gathered to form the Iternational Monetary Fund in 1944
* It is a stunning hotel with beautiful views
* All of us dreamed of celebrating an upcoming wedding here
<br>
<br>

```{r Day 3, message=FALSE,echo=FALSE}

wash_cold <- image_read("~/Documents/VT_Trip/VT_trip/mt_cold.jpg")
wash_road <- image_read("~/Documents/VT_Trip/VT_trip/Mt_wash_road.jpg")
wash_hotel <- image_read("~/Documents/VT_Trip/VT_trip/mt_wash_hotel.jpg")
tip_top <- image_read("~/Documents/VT_Trip/VT_trip/tip_top_hotel.jpg")


wash_cold

wash_road
tip_top
wash_hotel

leaflet() %>%
  addTiles() %>%
  addMarkers(lng = -71.303471, lat = 44.269733, label = 'Mt Washington') %>%
  addMarkers(lng = -71.439799, lat = 44.257311, label = 'Mt Washington Hotel')

```
<br>
<br>


### Day 4, July 2

* We loved Mt Washington a lot and decided to go up to the summit again
* Had lunch again in Littleton
* After lunch, took the Cog Wheel train up the Mountain
* The Cog Wheel train in New Hampshire is the first such mountain train
* It was built in 1868, it shows the vision and willpower of Slyvester Marsh
* It was a 45 minute journey up.
* Enjoyed the beautiful views from the mountain, hiked a little
* It appears that everybody in the group love mountain views and hikes

<br>
<br>


```{r, Day 4, message=FALSE,echo=FALSE, cache=FALSE}

mt_wash_cog <- image_read("~/Documents/VT_Trip/VT_trip/mt_wash_rail.jpg")
cog <- image_read("~/Documents/VT_Trip/VT_trip/cog_rail.jpg")

mt_wash_cog
cog

leaflet() %>%
  addTiles() %>%
  addMarkers(lng = -71.349975, lat = 44.270662, label = 'Cog Wheel Train')

```

<br>
<br>

### Day 5, July 3

* Started driving towards Canada
* The scenery between Vermont and Canada makes you feel like you are in Switzerland
* Border crossing was easy and drive to Montreal was without much difficulty
* But the weather was not the best we had hoped for.
* This was one of the hottest weeks in North America with temperatures reaching above 95'
* After lunch we visited the Basilica and started driving back to our House
* It cooled down in the evening.
* Enjoyed a relaxing evening on Lake Harvey, it was a beautiful end to the overall trip

<br>
<br>

```{r Day 5, message=FALSE,echo=FALSE, cache=TRUE}
mont <- image_read("~/Documents/VT_Trip/VT_trip/montreal.jpg")
basilica <- image_read("~/Documents/VT_Trip/VT_trip/basilica.jpg")

mont
basilica

```

<br>
<br>

```{r Day 6, message=FALSE,echo=FALSE, cache=TRUE}

fK_pepe <- image_read("~/Documents/VT_Trip/VT_trip/pepe_displ.jpg")
pizza <- image_read("~/Documents/VT_Trip/VT_trip/tom_pizza.jpg")
nyc_firewk <- image_read("~/Documents/VT_Trip/VT_trip/nyc_firework.jpg")

fK_pepe
pizza
nyc_firewk

```

### Day 6, July 4th Happy Independence Day

* Strated driving back to New York
* Had Frank Pepe Pizza(again)
* Reached New York City around 5.30 pm
* Watched Coco Movie and ate Kichdi and ice cream (Ben & Jerry's)
* Went to the rooftop and watched the July 4th Fireworks and Empire State Building

```{r Maps, message=FALSE,echo=FALSE}

leaflet() %>%
  addTiles() %>%
  addMarkers(lng = -72.136948, lat = 44.298359, label = 'Rental House') %>%
  addMarkers(lng = -71.798607, lat = 44.304781, label = 'Walmart') %>%
  addMarkers(lng = -71.773045, lat = 44.306430, label = 'Changs Thai') %>%
  addMarkers(lng = -71.771685  , lat = 44.305761, label = 'Inkwell Coffee') %>%
  addMarkers(lng = -71.770650  , lat = 44.304226, label = 'The Little Grille') %>%
  addMarkers(lng = -71.303471, lat = 44.269733, label = 'Mt Washington') %>%
  addMarkers(lng = -71.439799, lat = 44.257311, label = 'Mt Washington Hotel') %>%
  addMarkers(lng = -72.917228, lat = 41.303193, label = 'Frank Pepe\'s Pizza') %>%
  addMarkers(lng = -73.556172, lat = 45.504447, label = 'Notre Dame Basilica') %>%
  addMarkers(lng = -74.176998, lat = 40.690399, label = 'Newark Airport') %>%
  addMarkers(lng = -74.000541, lat = 40.761253, label = 'New York City')
  
  
  

```





